\documentclass[a4paper,10pt]{article}

\usepackage[left=0.7in,right=0.7in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{hyperref}

\hypersetup{
	colorlinks=true,
	urlcolor=MidnightBlue
}

\pagestyle{empty}

% Section Styling
\titleformat{\section}{
	\large\bfseries\color{MidnightBlue}
}{}{0em}{}[\titlerule]

\titlespacing{\section}{0pt}{10pt}{6pt}

% Custom Commands
\newcommand{\resumeItem}[1]{
	\item \small{#1}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{2pt}
	\begin{tabularx}{\textwidth}{X r}
		\textbf{#1} & \textcolor{gray}{#2} \\
		\textit{#3} & \textit{#4} \\
	\end{tabularx}
}

\begin{document}
	
	% ================= HEADER =================
	
	\begin{center}
		{\Huge \textbf{Brintha Theboral}} \\[6pt]
		
		\faPhone \ +91 12345 12345 \quad
		\faEnvelope \ \href{mailto:xxx@email.com}{xxx@email.com} \quad
		\faGithub \ \href{https://github.com/yyy}{github.com/yyy} \quad
		\faLinkedin \ \href{https://linkedin.com/in/zzz}{linkedin.com/in/zzz}
	\end{center}
	
	% ================= SUMMARY =================
	
	\section*{Profile Summary}
	
	Motivated Computer Science Engineering student passionate about Artificial Intelligence, full-stack development, and scalable software systems. Strong experience in machine learning projects, REST APIs, and technical documentation using LaTeX.
	
	% ================= EDUCATION =================
	
	\section*{Education}
	
	\resumeSubheading
	{ABC Institute of Technology}{2022 -- 2026}
	{B.E Computer Science Engineering}{CGPA: 8.9/10}
	
	\resumeSubheading
	{Velammal Higher Secondary School}{2020 -- 2022}
	{Higher Secondary Education}{92\%}
	
	% ================= SKILLS =================
	
	\section*{Technical Skills}
	
	\begin{itemize}[leftmargin=0.15in]
		\item{
			\textbf{Programming:} Python, C++, JavaScript, SQL
		}
		
		\item{
			\textbf{Frameworks:} React, Node.js, Flask
		}
		
		\item{
			\textbf{Tools:} Git, Docker, Linux, TeXstudio, VS Code
		}
		
		\item{
			\textbf{Core Areas:} Machine Learning, REST APIs, Data Structures
		}
	\end{itemize}
	
	% ================= PROJECTS =================
	
	\section*{Projects}
	
	\resumeSubheading
	{AI Resume Analyzer}{Jan 2025}
	{Python, NLP, Flask}{}
	
	\begin{itemize}[leftmargin=0.2in]
		\resumeItem{Built an AI-based resume screening system using Natural Language Processing techniques.}
		\resumeItem{Implemented keyword extraction and ATS score prediction modules.}
		\resumeItem{Improved matching accuracy by 18\% using TF-IDF vectorization.}
	\end{itemize}
	
	\resumeSubheading
	{Smart Traffic Prediction System}{Aug 2024}
	{Machine Learning, Streamlit}{}
	
	\begin{itemize}[leftmargin=0.2in]
		\resumeItem{Developed a traffic density prediction dashboard using regression models.}
		\resumeItem{Visualized real-time congestion analytics with interactive charts.}
	\end{itemize}
	
	% ================= EXPERIENCE =================
	
	\section*{Experience}
	
	\resumeSubheading
	{Machine Learning Intern -- TechNova Labs}{May 2025 -- Jul 2025}
	{Chennai, India}{}
	
	\begin{itemize}[leftmargin=0.2in]
		\resumeItem{Worked on customer churn prediction using classification algorithms.}
		\resumeItem{Optimized preprocessing pipelines reducing training time by 22\%.}
	\end{itemize}
	
	% ================= CERTIFICATIONS =================
	
	\section*{Certifications}
	
	\begin{itemize}[leftmargin=0.2in]
		\resumeItem{Machine Learning Specialization -- Coursera}
		\resumeItem{AWS Cloud Foundations}
		\resumeItem{Python for Data Science -- IBM}
	\end{itemize}
	
	% ================= ACHIEVEMENTS =================
	
	\section*{Achievements}
	
	\begin{itemize}[leftmargin=0.2in]
		\resumeItem{Finalist in National Level Hackathon among 500+ teams.}
		\resumeItem{Solved 400+ coding problems across LeetCode and CodeChef.}
	\end{itemize}
	
\end{document}